---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Your Name**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_long, aes(x = date, y = count/population, color = race)) +
  geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "AZ") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
ggplot(covid_data_long, aes(x = date, y = count/population, color = race)) +geom_point()
I observed that the percentage of infection is almost the same for all race, except the NHPI, which the percentage of infection of COVID has been increasing through the date.


2. Are there any conclusions you can draw?
The population of NHPI is small comparing to other race, however, a large portion has got COVID-19, in fact the percentage is increasing. This might indicate that Covid-19 has been favored to spread in certain environment which is closed to the living areas with large NHPI population. By closely looking at the reason of the increase of cases in NHPI population, we might be able to find out. 


3. What were you not able to do due to not having the R knowledge?
Due to not having the R knowledge, I felt hard to construct more graphs representing the data. For example it might be more easier to see specific state's data if I can create a histogram or pie chart.

4. What other data would be useful to better understand this data?
It might be useful to contain some other data such as temperature, population density given the area of state, and so on. Since the spreading of such diseases cannot just be analyze based on population, race or state, it should be also affecting by many other variables.(For example, place with higher temperature might cause more cases)